EvoSwarm: An Event-based Architecture for Multi-population Optimization Algorithms

### 2020-04-30 draft.tex
images moved
Rewriting paragraph to avoid, closes #12

However, in the field of evolutionary algorithms, this has been a slow
realization, from the origins where Salza and Ferrucci
\cite{salza2016approach,salza2016develop} proposed an architecture
that carried evolutionary algorithms to the cloud, developed further
in \cite{de2017parallel} which starts to introduce cloud native
aspects such as the use of messaging queues and CoreOS as an operating
system designed from the ground up for container utilization. The way
these containers are organized, however, is rather classical in
nature: a master-worker approach, communicated using RabbitMQ, where
replicated workers perform the tasks in parallel. They called their
approach AMQPGA, inspired by the protocol, AMQP, used by RabbitMQ, the
messaging system. Other EAs topologies have also been used in the
cloud: \cite{dziurzanski2020scalable} adapts an island model to a
container architecture, in a system that is functionally equivalent to
classical models, but with the added advantage of being easy to deploy
and run.

@@

% \subsection{Experiment 2}
% \label{sec:exp2results}

% \begin{figure*}[h!tb]
%     \begin{tabular}
%         {c@{\hspace*{-0.00001\textwidth}}
%          c@{\hspace*{-0.00001\textwidth}}
%          c@{\hspace*{-0.00001\textwidth}}
%         }
%     GA  &  PSO & GA \& PSO\\   
%     \includegraphics[width=0.33\textwidth]{GAOnly_f001}&
%     \includegraphics[width=0.33\textwidth]{PSOOnly_f001}&
%     \includegraphics[width=0.33\textwidth]{GAPSO_f001}\\

%     \includegraphics[width=0.33\textwidth]{GAOnly_f002}&
%     \includegraphics[width=0.33\textwidth]{PSOOnly_f002}&
%     \includegraphics[width=0.33\textwidth]{GAPSO_f002}\\

%     \includegraphics[width=0.33\textwidth]{GAOnly_f003}&
%     \includegraphics[width=0.33\textwidth]{PSOOnly_f003}&
%     \includegraphics[width=0.33\textwidth]{GAPSO_f003}\\

%     \includegraphics[width=0.33\textwidth]{GAOnly_f004}&
%     \includegraphics[width=0.33\textwidth]{PSOOnly_f004}&
%     \includegraphics[width=0.33\textwidth]{GAPSO_f004}\\

%     \includegraphics[width=0.33\textwidth]{GAOnly_f005}&
%     \includegraphics[width=0.33\textwidth]{PSOOnly_f005}&
%     \includegraphics[width=0.33\textwidth]{GAPSO_f005}\\
%     \end{tabular}
%     \vspace{-3ex}
%      \caption{
%  Scaling of runtime with dimension to reach certain target values $\Delta f$. Lines:
%  average runtime (aRT); Cross ($+$): median runtime of successful runs to reach
%  the most difficult target that was reached at least once (but not always);
%  Cross (\textcolor{red}{$\times$}): maximum number of f-evaluations in any trial. Notched boxes:
%  interquartile range with median of simulated runs; All values are divided by
%  dimension and plotted as $log_{10}$ values versus dimension. 
%  %Shown is the aRT for
%  %fixed values of $\Delta f = 10k$ with $k$ given in the legend. 
%  Numbers above aRT-symbols
%  (if appearing) indicate the number of trials reaching the respective target.
%  %The light thick line with diamonds indicates the best algorithm from BBOB 2009
%  %for the most difficult target. Horizontal lines mean linear scaling, slanted
%  %grid lines depict quadratic scaling.
%  }
%     \end{figure*}

%     \begin{figure}[h!tb]
%         \begin{tabular}
%             {c@{\hspace*{-0.00001\textwidth}}
%              c@{\hspace*{-0.00001\textwidth}}
%             }

%         \includegraphics[width=0.48\textwidth]{ppfigs_f001}&
%         \includegraphics[width=0.48\textwidth]{ppfigs_f002}\\

%         \includegraphics[width=0.48\textwidth]{ppfigs_f003}&
%         \includegraphics[width=0.48\textwidth]{ppfigs_f004}\\

%         \includegraphics[width=0.48\textwidth]{ppfigs_f005}&
%         \\
%         \end{tabular}
%         \vspace{-3ex}
%          \caption{Average running time (aRT in number of f-evaluations as $log_{10}$ value),
%           divided by dimension for target function value $10^{-8}$ versus dimension. 
%           Slanted grid lines indicate quadratic scaling with the dimension. 
%           Different symbols correspond to different algorithms given in the 
%           legend of $f_1$. Light symbols give the maximum number of 
%           function evaluations from the longest trial divided by dimension. 
%           Black stars indicate a statistically better result compared to 
%           all other algorithms with $p < 0.01$ and Bonferroni 
%           correction number of dimensions (six).}
%     \end{figure}

>>>>

However, in the field of evolutionary algorithms, this has been a slow
realization, from the origins where Salza and Ferrucci
\cite{salza2016approach,salza2016develop} proposed an architecture
that carried evolutionary algorithms to the cloud, and which were
developed further in the next paper \cite{de2017parallel}. These
papers started to introduce cloud native aspects such as the use of
messaging queues and CoreOS as an operating system designed from the
ground up for container utilization in the area of evolutionary
algorithms. The way these containers are managed, however, is rather
classical in nature from the point of view of distributed EC: a
master-worker approach, communicated using RabbitMQ (a messaging
queue), where replicated workers perform the tasks in parallel. They
called their approach AMQPGA, inspired by the protocol, AMQP, used by
RabbitMQ, the messaging system. This classical approach has been also
followed by other authors by using other EA ``classical'' topologies
in the cloud: \cite{dziurzanski2020scalable} adapts an island model to
a container architecture, in a system that is functionally equivalent
to classical models, but with the added advantage of being easy to
deploy and run.

@@
